### 2019-09-18 paper/spad_single/sections/hardware.tex
Camera alignment, distortion correction, working on supplement figure.

\subsection{Setup}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/hardware.jpeg}
  \caption{\textbf{Hardware setup}}
\end{figure}
\begin{itemize}
  \item{Description of hardware used}
  \item{Images of scenes used}
\end{itemize}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
  \caption{\textbf{Hardware results}}
\end{figure}

>>>>

\subsection{Setup}
\begin{figure}
  \includegraphics[width=\textwidth/2]{sections/figures/hardware.jpeg}
  \caption{\textbf{Hardware setup}}
\end{figure}
\begin{itemize}
  \item{Description of hardware used}
  \item{Images of scenes used}
\end{itemize}
% \begin{figure}
%  \includegraphics[width=\textwidth/2]{sections/figures/hardware_results.jpeg}
%  \caption{\textbf{Hardware results}}
% \end{figure}
%       "8_29_kitchen_scene",
%       "8_29_conference_room_scene",
%       "8_30_conference_room2_scene",
%       "8_30_Hallway",
%       "8_30_poster_scene",
%       "8_30_small_lab_scene",
\begin{figure*}[t!]
    \centering
    \begin{tabular}{p{5mm}ccccc}
      \multirow[t]{5}{=}[-1in]{\rotatebox[origin=rc]{90}{Kitchen Scene}} & Ground Truth & CNN & CNN Mean Rescaled & CNN Histogram Matched & \\
      &
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/gt_z_proj_crop.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/depth_colorbar.pdf}\\
      & RGB &  &  &  & \\
      &
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/rgb_cropped.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_kitchen_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_29_kitchen_scene/rmses.tex}& \\

      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 1}}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/gt_z_proj_crop.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/rgb_cropped.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_29_conference_room_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_29_conference_room_scene/rmses.tex}& \\

      \multirow[t]{3}{=}{\rotatebox[origin=c]{90}{Conference Room 2}}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/gt_z_proj_crop.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_depth_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/depth_colorbar.pdf}\\

      &
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/rgb_cropped.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_init_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[height=1.25in, width=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/z_pred_diff_fig.png}&
      \includegraphics[height=1.25in]{sections/figures/captured/midas/8_30_conference_room2_scene/diff_colorbar.pdf}\\
      & & \input{sections/figures/captured/midas/8_30_conference_room2_scene/rmses.tex}& \\ 
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN.
      Second row shows absolute difference between above estimates and ground truth.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}
\begin{figure*}[t!]
    \centering
    \begin{tabular}{ccccc}
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_init_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_pred_depth_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_Hallway/depth_colorbar.pdf}\\

      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/rgb_cropped.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_init_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_Hallway/z_pred_diff_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_Hallway/diff_colorbar.pdf}\\
      & \input{sections/figures/captured/midas/8_30_Hallway/rmses.tex}& \\

      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_depth_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_poster_scene/depth_colorbar.pdf}\\

      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/rgb_cropped.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_poster_scene/z_pred_diff_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_poster_scene/diff_colorbar.pdf}\\
      & \input{sections/figures/captured/midas/8_30_poster_scene/rmses.tex}& \\

      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/gt_z_proj_crop_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_depth_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_depth_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_small_lab_scene/depth_colorbar.pdf}\\

      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/rgb_cropped.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_init_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_med_scaled_diff_fig.png}&
      \includegraphics[width=1.25in]{sections/figures/captured/midas/8_30_small_lab_scene/z_pred_diff_fig.png}&
      \includegraphics[width=0.5in]{sections/figures/captured/midas/8_30_small_lab_scene/diff_colorbar.pdf}\\
      & \input{sections/figures/captured/midas/8_30_small_lab_scene/rmses.tex}\\

%      (a)&(b)&(c)&(d)&(e)\\
    \end{tabular}
    \caption{Captured results initialized using the MiDaS CNN. (a) RGB image.
      (b) Ground Truth Depth. (c) Initial Depth Estimate. (d) SPAD-median
      Rescaled Estimate. (e) SPAD Histogram Matched Estimate.}
    \label{fig:midas_captured}
%    \vspace{-1.5em}
\end{figure*}
